---
title: "Extended Installation Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extended Installation Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

*Talk* enables users access to HuggingFace Transformers in R through the R-package [reticulate](https://rstudio.github.io/reticulate/) as an interface to [Python](https://www.python.org/), and the python packages [torch](https://pytorch.org/) and [transformers](https://huggingface.co/docs/transformers/index). So it's important to install both the talk-package and a python environment with the talk required python packages that the talk-package can use. </br></br> The recommended way is to use `talkrpp_install()` to install a mini conda environment with talk required python packages, and `talkrpp_initialize` to initialize it.

## Conda environment

```{r extended_installation_condaenv, eval = FALSE}
library(talk)
library(reticulate)

# Install text required python packages in a conda environment (with defaults).
text::talkrpp_install()

# Show available conda environments.
reticulate::conda_list()

# Initialize the installed conda environment.
# save_profile = TRUE saves the settings so that you don't have to run talkrpp_initialize() after restarting R. 
text::talkrpp_initialize(save_profile = TRUE)

# Test so that the text package work.
wav_path <- system.file("extdata/",
                        "test_short.wav",
                        package = "talk")
wav_path

emb_test <- talk::talkEmbed(
  talk_filepaths = wav_path
)

```


